Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-06-02 manuscript.Rmd
clean affect data

df_personality <- 
df_personality %>% 
  pivot_longer(cols = judgment_trait1:informant_trait26,
               names_to = c("trait", "item"),
               names_sep = "_",
               values_to = "rating") %>% 
  mutate(item = parse_number(item)) %>% # could not write the correct regex :(
  pivot_wider(names_from = "trait",
              values_from = "rating") %>% 
  right_join(., trait_norms, by = "item") %>% 
  mutate(self_dist = target - self_norm,
         inf_dist = informant - inf_norm,
         across(c(InsecAtt:Trust, self_norm:inf_dist), 
                scale, scale = FALSE, center = TRUE)
         )

>>>>

df_personality <- # create final df for analyses
df_personality %>% 
  pivot_longer(cols = judgment_trait1:informant_trait26,
               names_to = c("trait", "item"),
               names_sep = "_",
               values_to = "rating") %>% 
  mutate(item = parse_number(item)) %>% # could not write the correct regex :(
  pivot_wider(names_from = "trait",
              values_from = "rating") %>% 
  right_join(., trait_norms, by = "item") %>% 
  mutate(self_dist = target - self_norm,
         inf_dist = informant - inf_norm,
         across(c(InsecAtt:Trust, self_norm:inf_dist), 
                scale, scale = FALSE, center = TRUE)
         )
## Affect
df_affect <- 
  df %>% 
  select(perceiver_id:group_id,
         target_affect1:judgment_affect120)

affect_norms <- # average values
  df_affect %>% 
  select(target_affect1:target_affect120) %>% 
  map_df(., mean, na.rm = TRUE) %>% 
  pivot_longer(., cols = everything(),
               names_to = "item",
               names_pattern = "(\\d+)$",
               values_to = "norm") %>% 
  mutate(item = as.numeric(item))

df_affect <- 
  df_affect %>% 
  pivot_longer(cols = target_affect1:judgment_affect120,
               names_to = c("affect", "item"),
               names_sep = "_",
               values_to = "rating") %>% 
  mutate(item = parse_number(item)) %>% 
  pivot_wider(names_from = "affect",
              values_from = "rating") %>% 
  right_join(., affect_norms, by = "item") %>% 
  mutate(self_dist = target - norm,
         across(norm:self_dist, scale, scale = FALSE, center = TRUE)
         )
